\section{Implementation Stack and Data Engineering}
\label{sec:implementation_stack}

\subsection{Analytical Engine: DuckDB}\textbf{DuckDB}, an in-process OLAP database, served as the primary engine for high-speed data transformation. By utilizing vectorized execution and columnar storage, it bypassed traditional RDBMS bottlenecks, allowing for sub-second aggregation of 39,000 milestones. Specifically, DuckDB facilitated a zero-copy pipeline to extract raw logs from MySQL and serialize them directly into Python DataFrames for analysis.

\subsection{Record Filtering and Cardinality Constraints}To ensure the integrity of the $A \rightarrow B$ relationship, we excluded transactions containing only a single milestone. Because ARM metrics require disjoint sets to establish predictive logic, a basket cardinality of $n \ge 2$ is mandatory. This filtering process resulted in a refined dataset:

\begin{itemize}\item \textbf{Session Basket \# of Records:} 20772\item \textbf{User Basket \# of Records:} 2352\end{itemize}

This reduction refocused computational resources on discovering multi-step behavioral sequences rather than isolated, non-associative actions. For that anlaysis of schema, relationships, joins, etc. were conducted, code related to that can be found in python scripts in \textbf{code/} of \href{https://github.com/bhavik-knight/5580-dm-a3-association}{GitHub}.


\subsection{Algorithmic Framework: mlxtend}Frequent pattern mining was implemented using the \textbf{mlxtend} library \cite{raschka_mlxtend}. According to the documentation, \textit{mlxtend} provides an industry-standard interface for association rule discovery, supporting efficient boolean matrix transformations. We utilized its mathematically rigorous implementations of both \textbf{Apriori} and \textbf{FP-Growth} to calculate support, confidence, and lift across the SimplyCast dataset. The study mainly focus on using\textbf{Apriori} algorithm, however \textbf{FP-Growth} algorithm is discussed in \autoref{sec:app_a}